### 2014-09-24 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to report

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
\caption{Front (left) and rear (right) of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/SMV_Exterior_Meshes}
\caption[Rear-left side of the structure within the computational domain.]
{Rear-left side of the structure within the computational domain (with multiple meshes).}
\label{fig:mult_mesh}
\end{figure}

>>>>

As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft). To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure. The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft). A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 5.1 million computational cells. As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm. Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.

\begin{figure}[!ht]
\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
\caption{Front (top) and rear (bottom) of the structure with a 10~cm computational mesh.}
\label{fig:SMV_exterior_grid}
\end{figure}

@@

\begin{figure}[!ht]
\includegraphics[width=6.5in]{../Figures/SMV_Exterior_Meshes}
\caption[Rear-left side of the structure within the computational domain.]
{Rear-left side of the structure within the computational domain with multiple meshes.}
\label{fig:mult_mesh}
\end{figure}
